Supplementary Material

### 2022-02-28 analysis/paper/paper.Rmd
add S prefix to all tables and figs in supp mat
submission to journal

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  #fig.path = "frontiers/figures/",
  fig.path = "../figures/",
  fig.align = "center",
  #fig.ext = "jpg",
  fig.pos = "H",
  dpi = 300) 
library(tidyverse)
library(broom)
library(here)
library(patchwork)
# load R scripts
source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/tables.R"))
source(here("analysis/scripts/figures.R"))
source(here("analysis/scripts/amylase-assay.R"))
## Compile refs.bib using rbbt package ##
#cite_keys <- rbbt::bbt_detect_citations(here("analysis/paper/paper.Rmd")) 
#cite_keys <- unlist(cite_keys, use.names = FALSE)
#rbbt::bbt_write_bib(here("analysis/paper/refs.bib"), keys = cite_keys, overwrite = T, translator = "bibtex")
# ## end refs.bib ##
# 
# ## Word count ##
# wd_count <- wordcountaddin::word_count()
cor_r <- signif(count_cor$estimate, 3)
cor_ci <- signif(count_cor$conf.int, 3)
cor2_r <- signif(count_cor$estimate, 3)
cor2_ci <- signif(count_cor$conf.int, 3)
```

@@

# Tables

@@

# Figure Captions

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  #fig.path = "frontiers/figures/",
  fig.path = "../figures/",
  fig.align = "center",
  #fig.ext = "jpg",
  fig.pos = "H",
  dpi = 300) 
library(tidyverse)
library(broom)
library(here)
library(patchwork)
# load R scripts
source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/tables.R"))
source(here("analysis/scripts/figures.R"))
source(here("analysis/scripts/amylase-assay.R"))
## Compile refs.bib using rbbt package ##
cite_keys <- rbbt::bbt_detect_citations(here("analysis/paper/paper.Rmd")) 
cite_keys <- unlist(cite_keys, use.names = FALSE)
rbbt::bbt_write_bib(here("analysis/paper/refs.bib"), keys = cite_keys, overwrite = T, translator = "bibtex")
# ## end refs.bib ##
# 
# ## Word count ##
# wd_count <- wordcountaddin::word_count()
cor_r <- signif(count_cor$estimate, 3)
cor_ci <- signif(count_cor$conf.int, 3)
cor2_r <- signif(count_cor$estimate, 3)
cor2_ci <- signif(count_cor$conf.int, 3)
```

@@

# Tables {-}

@@

# Figures {-}

### 2022-02-28 analysis/paper/paper.tex
submission to journal

\usepackage{float}
\let\origfigure\figure
\let\endorigfigure\endfigure
\renewenvironment{figure}[1][2] {
    \expandafter\origfigure\expandafter[H]
} {
    \endorigfigure
}
\usepackage{float}

@@

Despite this, our knowledge of dental calculus and the incorporation pathways of
the various markers is limited (Radini et al., 2017), as is our
knowledge of information-loss caused by these pathways. Additionally, the methods
we use to extract and analyse dental calculus, and make inferences on past diets
represent another potential source of bias. Studies on both archaeological and
modern individuals have explored these biases in more detail.
Extraction methods were tested
by Tromp and colleagues (2017), specifically regarding
decalcification using HCl or EDTA.
The authors found significantly more starches with the EDTA extraction method
than the HCl extraction method; however, as noted by the authors, comparisons
involving archaeological calculus are problematic due to variability between and
within individuals.
Studies conducted on modern humans (Leonard et al., 2015)
and non-human primates (Power et al., 2015),
have explored how well microremains (phytoliths and starches)
extracted from dental calculus represent the actual dietary intake.
These studies are justifiably limited,
despite meticulous documentation and observation, due to unknown variables and
uncertainty involved when studying living organisms. Dental calculus is a complex
oral biofilm with a multifactorial aetiology and variable formation rates both
within and between individuals (Jepsen et al., 2011; Haffajee et al., 2009),
contributing to
the stochasticity of starch representation being observed in numerous studies.
Additionally, the concentration of oral \(\alpha\)-amylase differs both between and
within individuals (Froehlich et al., 1987; Nater et al., 2005),
causing different rates of hydrolysis of the starch granules present in the oral
cavity. Add to this the effects of the many different methods
of starch processing, as well as post-depositional processes that are still being
explored (García-Granero, 2020), and it becomes clear that using
dental calculus to reconstruct diet is a highly unpredictable process.

@@

Starch treatments were initiated on day 9 to avoid starch granule counts being
affected by \(\alpha\)-amylase hydrolysis from saliva inoculation days.
An \(\alpha\)-amylase (EC 3.2.1.1) activity
assay was conducted to confirm that no amylase was present in the system before
starch treatments started. Starch treatments replaced sucrose treatments, occurring twice per day
for six minutes. The starch treatments involved transferring the substrata to a
new plate containing a 0.25\% (w/v) starch from potato (Roth 9441.1) solution, a 0.25\% (w/v) starch from wheat (Sigma S5127) solution, and a 0.5\% (w/v) mixture of equal
concentrations (w/v) wheat and potato. All starch treatments were created in dH\textsubscript{2}O
with 5\% (w/v) sucrose. Before transferring biofilm samples to the starch treatment
plate, the plates were agitated to keep the starches in suspension in the
solutions. During treatments, the rpm was increased to 60 to facilitate contact
between starch granules and biofilms.

@@

An \(\alpha\)-amylase (EC 3.2.1.1) activity assay was conducted on artificial
saliva samples collected from the plate wells on days 3, 6, 8, 9, 10, 12, and 14.
Whole saliva samples were collected on days 0, 3, and 5 as positive controls.
Collected samples were stored at 4°C until the assay was conducted on day 18.
All samples and standard curves were run in triplicates on two separate plates.
Positive control saliva samples were compared against a standard curve containing
H\textsubscript{2}O, while artificial saliva samples were compared against a standard curve
containing sterile artificial saliva (due to the colour of artificial saliva).
Two photometric readings were conducted for each plate with a 540 nm filter on a
Multiskan FC Microplate Photometer (Thermo Scientific 51119000).
The protocol is a modified version of an Enzymatic Assay of \(\alpha\)-Amylase
(\url{https://www.sigmaaldrich.com/NL/en/technical-documents/protocol/protein-biology/enzyme-activity-assays/enzymatic-assay-of-a-amylase}) (Bernfeld, 1955), which measures the amount of
maltose released from starch by \(\alpha\)-amylase activity. Results are reported
in units (U) per mL enzyme, where 1 U releases 1 \(\mu\)mole of maltose in 6 minutes.
The detailed protocol can be found here: \url{https://www.protocols.io/view/amylase-activity-bw8jphun}.

@@

It was not possible to differentiate between potato and
wheat starches smaller than ca. 10 \(\mu\)m. These were counted as wheat,
as we assumed that the majority of the small granules were wheat. We make this
assumption based on the counts of small starches in the wheat-only and potato-only
solutions. Of the total amount of small starches in these two solutions,
99.2\%
are from wheat.

@@

Here, we have provided a method for exploring the incorporation of dietary
starches into the mineral matrix of a dental calculus biofilm model. Our results show
that a very low proportion of the starches exposed to the biofilm during growth are
retained in the mineral matrix, and that the size of the starch granules
may affect the likelihood of incorporation. The proportions of starch granules
(of all sizes) present in the extracted samples were similar across all treatments
(0.06\% to 0.16\%),
despite large differences in absolute granule counts between wheat
(mean = 25,404,000)
and potato
(mean = 3,016,000)
solutions.\\
The absolute counts, however, differed more visibly between treatments and was
proportional with the total count of granules in the treatment solutions. Wheat
and mixed solutions had the highest absolute mean count of starch granules, and
also had the highest absolute mean count of starch granules extracted from the
dental calculus
(Tables \ref{tab:solution-count-tbl} and \ref{tab:sample-count-tbl}).
This suggests that the starches that are more frequently consumed will be present
in higher quantities in the dental calculus, at least prior to inhumation and
degradation in the burial environment.
Despite the low proportion of granules recovered from the model calculus
(0.06\% to 0.16\%),
the absolute counts were still substantially greater than counts recovered from
archaeological remains
(Tromp and Dudgeon, 2015; Tromp et al., 2017; Wesolowski et al., 2010), which could in part be due to the
lack of oral amylase activity in our model.

We have also shown that the size of the starch granules influences the likelihood
of incorporation into the calculus. Starch granules larger than 20 \(\mu\)m in
maximum length were underrepresented in the calculus samples compared to the original
starch solutions, an effect that was consistent across all three treatments,
while medium granules (10--20 \(\mu\)m) were often over-represented
(Table \ref{tab:sample-prop-tbl},
and
Figure \ref{fig:ratio-plots}).
Large potato granules were most affected, potentially because of the greater
size-range. They can reach up to 100 \(\mu\)m in maximum length, whereas wheat
granules generally only reach up to 35 \(\mu\)m
(Gismondi et al., 2019; Haslam, 2004; Seidemann, 1966, 174--176).
Granule morphology may also play a role. Large wheat granules
are lenticular and have a larger surface area compared
to volume, whereas large potato granules are ovoid and have a larger volume
compared to surface area
(van de Velde et al., 2002; Jane et al., 1994; Reichert, 1913, 364--365; Seidemann, 1966, 174--176).
Another potentially important factor
from our results is the size of the calculus deposit. We found a
strong positive correlation between biofilm size and retained
starch granules (Figure \ref{fig:cor-plot}A);
a result that contradicts findings from archaeological contexts
(Wesolowski et al., 2010; Dudgeon and Tromp, 2014).
When the concentration of starch granules
per mg calculus is considered, the correlation is weaker, but still present
(Figure \ref{fig:cor-plot}B).
While the larger deposits contain a higher absolute count, our findings also suggest
that they contain a slightly higher concentration of starches. This may also explain
the lower mean retention of starch granules in mixed treatments compared to
wheat treatments. Wheat treatment samples (mean = 5.53 mg) were on average larger than mixed treatment samples (mean = 4.28 mg) (Table \ref{tab:anova-tbl}); and while mixed treatment solutions contained the highest mean overall
granule counts, wheat treatment samples had the highest mean starch retention.
Further research is needed to determine why this differs from previous archaeological
findings.

Previous research conducted on dental calculus from contemporary humans and non-human
primates suggest a high level of stochasticity involved in the retention of
starch granules in dental calculus, and that starch granules extracted from dental
calculus are underrepresented with regard
to actual starch intake, which is consistent with our findings (illustrated by high
standard deviations and low proportional incorporation).
Leonard and colleagues (2015) found individual
calculus samples to be a poor predictor of diet in a population, as many of the
consumed plants were missing from some individual samples, but were present in others.\\
Power and colleagues (2015)
presented similar findings in non-human primates, where phytoliths were more
representative of individual diets than starch granules.
The size bias is also consistent with the findings by Power and colleagues
(2015),
who found that plants producing starches 10--20 \(\mu\)m in
size were over-represented; however, the representation of granules larger than
20 \(\mu\)m in their study is unclear.

@@

\hypertarget{tables}{%
\section{Tables}\label{tables}}

@@

\hypertarget{figure-captions}{%
\section{Figure Captions}\label{figure-captions}}

>>>>

\usepackage{float}

@@

Despite this, our knowledge of dental calculus and the incorporation pathways of
the various markers is limited (Radini et al., 2017), as is our
knowledge of information-loss caused by these pathways. Additionally, the methods
we use to extract and analyse dental calculus, and make inferences on past diets
represent another potential source of bias. Studies on both archaeological and
modern individuals have explored these biases in more detail.
Extraction methods were tested
by Tromp and colleagues (2017), specifically regarding
decalcification using HCl or EDTA.
The authors found significantly more starches with the EDTA extraction method
than the HCl extraction method; however, as noted by the authors, comparisons
involving archaeological calculus are problematic due to variability between and
within individuals.
Studies conducted on modern humans (Leonard et al., 2015)
and non-human primates (Power et al., 2015),
have explored how well microremains (phytoliths and starches)
extracted from dental calculus represent the actual dietary intake.
These studies are justifiably limited,
despite meticulous documentation and observation, due to unknown variables and
uncertainty involved in this kind of \emph{in vivo} research. Dental calculus is a complex
oral biofilm with a multifactorial aetiology and variable formation rates both
within and between individuals (Jepsen et al., 2011; Haffajee et al., 2009),
contributing to
the stochasticity of starch representation being observed in numerous studies.
Additionally, the concentration of oral \(\alpha\)-amylase differs both between and
within individuals (Froehlich et al., 1987; Nater et al., 2005),
causing different rates of hydrolysis of the starch granules present in the oral
cavity. Add to this the effects of the many different methods
of starch processing, as well as post-depositional processes that are still being
explored (García-Granero, 2020), and it becomes clear that using
dental calculus to reconstruct diet is a highly unpredictable process.

@@

Starch treatments were initiated on day 9 to avoid starch granule counts being
affected by \(\alpha\)-amylase hydrolysis from saliva inoculation days.
An \(\alpha\)-amylase (EC 3.2.1.1) activity
assay was conducted to confirm that no amylase was present in the model before
starch treatments started. Starch treatments replaced sucrose treatments, occurring twice per day
for six minutes. The starch treatments involved transferring the substrata to a
new plate containing a 0.25\% (w/v) starch from potato (Roth 9441.1) solution, a 0.25\% (w/v) starch from wheat (Sigma S5127) solution, and a 0.5\% (w/v) mixture of equal
concentrations (w/v) wheat and potato. All starch treatments were created in dH\textsubscript{2}O
with 5\% (w/v) sucrose. Before transferring biofilm samples to the starch treatment
plate, the plates were agitated to keep the starches in suspension in the
solutions. During treatments, the rpm was increased to 60 to facilitate contact
between starch granules and biofilms.

@@

An \(\alpha\)-amylase (EC 3.2.1.1) activity assay was conducted on artificial
saliva samples collected from the plate wells on days 3, 6, 8, 9, 10, 12, and 14.
Whole saliva samples were collected on days 0, 3, and 5 as positive controls.
Collected samples were stored at 4°C until the assay was conducted on day 18.
All samples and standard curves were run in triplicates on two separate plates.
Positive control saliva samples were compared against a standard curve containing
H\textsubscript{2}O, while artificial saliva samples were compared against a standard curve
containing stock AS (due to the colour of artificial saliva).
Two photometric readings were conducted for each plate with a 540 nm filter on a
Multiskan FC Microplate Photometer (Thermo Scientific 51119000).
The protocol is a modified version of an Enzymatic Assay of \(\alpha\)-Amylase
(\url{https://www.sigmaaldrich.com/NL/en/technical-documents/protocol/protein-biology/enzyme-activity-assays/enzymatic-assay-of-a-amylase}) (Bernfeld, 1955), which measures the amount of
maltose released from starch by \(\alpha\)-amylase activity. Results are reported
in units (U) per mL enzyme, where 1 U releases 1 \(\mu\)mole of maltose in 6 minutes.
The detailed protocol can be found here: \url{https://www.protocols.io/view/amylase-activity-bw8jphun}.

@@

It was not possible to differentiate between potato and
wheat starches smaller than ca. 10 \(\mu\)m. These were counted as wheat,
as we assumed that the majority of the small granules were wheat. We make this
assumption based on the counts of small starches in the wheat-only and potato-only
solutions. Of the combined amount of small starches in these two solutions,
99.2\%
are from wheat.

@@

Here, we have provided a method for exploring the incorporation of dietary
starches into the mineral matrix of a dental calculus biofilm model. Our results show
that a very low proportion of the starches exposed to the biofilm during growth are
retained in the mineral matrix, and that the size of the starch granules
may affect the likelihood of incorporation. The proportions of starch granules
(of all sizes) present in the extracted samples were similar across all treatments
(0.06\% to 0.16\%),
despite large differences in absolute granule counts between wheat
(mean = 25,404,000)
and potato
(mean = 3,016,000)
solutions.\\
The absolute counts, however, differed more visibly between treatments and was
proportional with the total count of granules in the treatment solutions. Wheat
and mixed solutions had the highest absolute mean count of starch granules, and
also had the highest absolute mean count of starch granules extracted from the
dental calculus
(Tables \ref{tab:solution-count-tbl} and \ref{tab:sample-count-tbl}).
This suggests that the starches that are more frequently consumed will be present
in higher quantities in the dental calculus, at least prior to inhumation and
degradation in the burial environment.
Despite the low proportion of granules recovered from the model calculus
(0.06\% to 0.16\%),
the absolute counts were still substantially greater than counts recovered from
archaeological remains
(Tromp and Dudgeon, 2015; Tromp et al., 2017; Wesolowski et al., 2010), which could in part be due to the
lack of oral amylase activity in our model.
Previous research conducted on dental calculus from contemporary humans and non-human
primates suggest a high level of stochasticity involved in the retention of
starch granules in dental calculus, and that starch granules extracted from dental
calculus are underrepresented with regard
to actual starch intake, which is consistent with our findings (illustrated by high
standard deviations and low proportional incorporation).
Leonard and colleagues (2015) found individual
calculus samples to be a poor predictor of diet in a population, as many of the
consumed plants were missing from some individual samples, but were present in others.\\
Power and colleagues (2015)
presented similar findings in non-human primates, where phytoliths were more
representative of individual diets than starch granules.
The size bias is also consistent with the findings by Power and colleagues
(2015),
who found that plants producing starches 10--20 \(\mu\)m in
size were over-represented; however, the representation of granules larger than
20 \(\mu\)m in their study is unclear.

We have also shown that the size of the starch granules influences the likelihood
of incorporation into the calculus. Starch granules larger than 20 \(\mu\)m in
maximum length were underrepresented in the calculus samples compared to the original
starch solutions, an effect that was consistent across all three treatments. Medium
granules (10--20 \(\mu\)m) were often over-represented
(Table \ref{tab:sample-prop-tbl},
and
Figure \ref{fig:ratio-plots}).
Large potato granules were most affected, potentially because of the greater
size-range. They can reach up to 100 \(\mu\)m in maximum length, whereas wheat
granules generally only reach up to 35 \(\mu\)m
(Gismondi et al., 2019; Haslam, 2004; Seidemann, 1966, 174--176).
Granule morphology may also play a role. Large wheat granules
are lenticular and have a larger surface area compared
to volume, whereas large potato granules are ovoid and have a larger volume
compared to surface area
(van de Velde et al., 2002; Jane et al., 1994; Reichert, 1913, 364--365; Seidemann, 1966, 174--176).
Another potentially important factor
from our results is the size of the calculus deposit. We found a
strong positive correlation between biofilm size and retained
starch granules (Figure \ref{fig:cor-plot}A);
a result that contradicts findings from archaeological contexts
(Wesolowski et al., 2010; Dudgeon and Tromp, 2014).
When the concentration of starch granules
per mg calculus is considered, the correlation is weaker, but still present
(Figure \ref{fig:cor-plot}B).
While the larger deposits contain a higher absolute count, our findings also suggest
that they contain a slightly higher concentration of starches. This may also explain
the lower mean retention of starch granules in mixed treatments compared to
wheat treatments. Wheat treatment samples (mean = 5.53 mg) were on average larger than mixed treatment samples (mean = 4.28 mg) (Table \ref{tab:anova-tbl}); and while mixed treatment solutions contained the highest mean overall
granule counts, wheat treatment samples had the highest mean starch retention.
Further research is needed to determine why this differs from previous archaeological
findings.

@@

\clearpage

\hypertarget{tables}{%
\section*{Tables}\label{tables}}
\addcontentsline{toc}{section}{Tables}

@@

\hypertarget{figures}{%
\section*{Figures}\label{figures}}
\addcontentsline{toc}{section}{Figures}

### 2022-02-28 analysis/supplementary-materials/supp-mat.Rmd
submission to journal

---
title: "Supplementary Material"
output:
  bookdown::html_document2:
    df_print: paged
    toc: yes
    toc_float: yes
  bookdown::pdf_document2:
    toc: yes
    df_print: kable
---

```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(patchwork)
source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/figures.R"))
source(here("analysis/scripts/tables.R"))
source(here("analysis/scripts/amylase-assay.R"))
#raw_data_samples <- read_csv(here("analysis/data/raw_data/starch_counts.csv"))
#raw_data_solutions <- read_csv(here("analysis/data/raw_data/solution_counts.csv"))
```

@@

```{r plate-lid-1, fig.cap="The 24 deepwell plate and the lid with pegs (substrata)"}
knitr::include_graphics(here("analysis/supplementary-materials/figures/plate_lid_side.jpg"))
```

```{r plate-lid-2, fig.cap="The 24 deepwell plate with the lid (almost) on."}
knitr::include_graphics(here("analysis/supplementary-materials/figures/plate_lid_on.jpg"))
```

@@

```{r img-1, echo=FALSE, fig.cap="Image of starch granules extracted from a potato treatment sample"}
knitr::include_graphics(here("analysis/supplementary-materials/figures/starches_w_bar.jpg"))
```

```{r img-2}
knitr::include_graphics(here("analysis/supplementary-materials/figures/SNAP-103412-0006.jpg"))
```

```{r img-3, fig.cap="Microscope image of wheat starch from a wheat treatment sample."}
knitr::include_graphics(here("analysis/supplementary-materials/figures/SNAP-164650-0012.jpg"))
```

@@

```{r amylase-plt1-read1}
plt1_ph1_result %>%
  knitr::kable("Amylase activity in U/mL for plate 1, photometric read 1.")
```

```{r amylase-plt1-read2}
plt1_ph2_result %>%
  knitr::kable("Amylase activity in U/mL for plate 1, photometric read 2.")
```

```{r amylase-plt2-read1}
plt2_ph1_result %>%
  knitr::kable("Amylase activity in U/mL for plate 2, photometric read 1.")
```

```{r amylase-plt2-read2}
plt2_ph2_result %>%
  knitr::kable("Amylase activity in U/mL for plate 2, photometric read 2.")
```

@@

```{r cor-plot, warning=FALSE, fig.cap="Scatter plot of sample weight and standardised starch count by z-score for separated treatments."}
pl_cor
```

```{r cor-plot2, warning=FALSE, fig.cap="Scatter plot of sample weight in mg and standardised count of starch grains per mg calculus."}
pl_cor2
```

>>>>

---
title: "Supplementary Material"
output:
  bookdown::pdf_document2:
    toc: yes
    df_print: kable
    extra_dependencies: ["float"]
  bookdown::html_document2:
    df_print: paged
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE,
                      fig.pos = "H",
                      dpi = 300)
library(here)
library(tidyverse)
library(patchwork)
source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/figures.R"))
source(here("analysis/scripts/tables.R"))
source(here("analysis/scripts/amylase-assay.R"))
#raw_data_samples <- read_csv(here("analysis/data/raw_data/starch_counts.csv"))
#raw_data_solutions <- read_csv(here("analysis/data/raw_data/solution_counts.csv"))
```

@@

```{r plate-lid-1, fig.cap="The 24 deepwell plate and the lid with pegs (substrata)", echo=FALSE}
knitr::include_graphics(here("analysis/supplementary-materials/figures/plate_lid_side.jpg"))
```

```{r plate-lid-2, fig.cap="The 24 deepwell plate with the lid (almost) on.", echo=FALSE}
knitr::include_graphics(here("analysis/supplementary-materials/figures/plate_lid_on.jpg"))
```

@@

```{r img-2, fig.cap="Microscope image of wheat starch from a Potato treatment sample.", echo=FALSE, out.width="80%"}
knitr::include_graphics(here("analysis/supplementary-materials/figures/SNAP-103412-0006.jpg"))
```

```{r img-3, fig.cap="Microscope image of wheat starch from a wheat treatment sample.", echo=FALSE, out.width="80%"}
knitr::include_graphics(here("analysis/supplementary-materials/figures/SNAP-164650-0012.jpg"))
```

@@

```{r amylase-plt1-read1, echo=FALSE}
plt1_ph1_result %>%
  knitr::kable(caption = "Amylase activity in U/mL for plate 1, photometric read 1.")
```

```{r amylase-plt1-read2, echo=FALSE}
plt1_ph2_result %>%
  knitr::kable(caption = "Amylase activity in U/mL for plate 1, photometric read 2.")
```

```{r amylase-plt2-read1, echo=FALSE}
plt2_ph1_result %>%
  knitr::kable(caption = "Amylase activity in U/mL for plate 2, photometric read 1.")
```

```{r amylase-plt2-read2, echo=FALSE}
plt2_ph2_result %>%
  knitr::kable(caption = "Amylase activity in U/mL for plate 2, photometric read 2.")
```

@@

```{r cor-plot, warning=FALSE, fig.cap="Scatter plot of sample weight and standardised starch count by z-score for separated treatments.", echo=FALSE}
pl_cor
```

```{r cor-plot2, warning=FALSE, fig.cap="Scatter plot of sample weight in mg and standardised count of starch grains per mg calculus.", echo=FALSE}
pl_cor2
```
